Verifying Concurrent Search Structure Templates for C Programs using VST

### 2023-04-10 concurrency/CONCUR 2023/paper.tex
add  command for Lennart

% comments from authors 
\newcommand{\than}[1]{\textbf{\textcolor{blue}{[ Than: #1]}}}

@@

@@

@@

We need to instantiate $\nodeboxrep$ (the resources associated with each client thread) and $\treerep$ (the abstract representation of the data structure), and show how they interact to access and update the state of the data structure for each call. In a lock-based implementation, $\nodeboxrep$ serves as a pointer to the root node's lock, and acquiring this lock allows the thread to access more elements within the data structure. As previously mentioned, the \lstinline{pn} struct comprises two nodes of type \lstinline{tree_t}: the \lstinline{p} field, which denotes the current node, and the \lstinline{n} field, which represents the next node. The resources $\texttt{R}$, parameterized by a node pointer, describes the concrete information about a node. The lock invariant $\lockinv$ predicate asserts that there exists a lock that protects the resources.

\subsection{Give-up Template}

>>>>

% comments from authors 
\newcommand{\than}[1]{\textbf{\textcolor{blue}{[ Than: #1]}}}
\newcommand{\lb}[1]{\textbf{\textcolor{red}{[ Lennart: #1]}}}

@@

\lb{say something}

@@

$$\forall \texttt{t}.\ \left\langle \nodeboxrep \texttt{(pn)} 
%\ast \lockinv \texttt{(pn->p->lock,R'}) 
\ast \texttt{R(pn->p)} \ | \ \treerep\ \texttt{t} \right\rangle $$
$$\texttt{traverse(pn, k)}$$
$$\left\langle \texttt{n'}.\ \nodeboxrep \texttt{(pn)} \
%ast \lockinv \texttt{(pn->n'->lock,R')} 
\ast \texttt{R(pn->n')} \ast (\texttt{k} \in \texttt{range})
\ |\ \treerep\ \texttt{t} \right\rangle$$

We need to instantiate $\nodeboxrep$ (the resources associated with each client thread) and $\treerep$ (the abstract representation of the data structure), and demonstrate how they interact to access and update the state of the data structure for each call. In a lock-based implementation, $\nodeboxrep$ serves as a pointer to the root node's lock, and acquiring this lock allows the thread to access more elements within the data structure. As previously mentioned, the \lstinline{pn} struct consists of two nodes of type \lstinline{tree_t}: the \lstinline{p} field, which denotes the current node, and the \lstinline{n} field, which represents the next node. The resources $\texttt{R}$, parameterized by a node pointer, describe the concrete information about a node. The lock invariant $\lockinv$ predicate asserts that a lock exists to protect the resources.

\subsection{Give-up Template}
Moving forward with the proofs, we define the following specification for the traverse function within the give-up template:

@@
